---
title: "LM with prediction"
author: "Maryana Maayah"
date: "11/21/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tigerstats)
library(tidyverse)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

```{r}
dataF <- read.csv(file="http://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE) 
```

## Model 1
  
```{r}
Model1=lm(SIMS~ARM,data=dataF)
summary(Model1)
NewDF=data.frame(ARM=88,GRIP=94)
predict(Model1,NewDF,interval="prediction")
```
  Adjusted R squared = 0.47
  Fit= 0.71, CI= (-1.73,3.14) 
  
## Model 2
  
```{r}
Model2=lm(SIMS~GRIP,data=dataF)
summary(Model2)
NewDF=data.frame(ARM=88,GRIP=94)
predict(Model2,NewDF,interval="prediction")
```
  Adjusted R squared = 0.41
  Fit= -0.54, CI= (-3.11,2.04)
  
## Model 3
  
```{r}
Model3=lm(SIMS~ARM+GRIP,data=dataF)
summary(Model3)
NewDF=data.frame(ARM=88,GRIP=94)
predict(Model3,NewDF,interval="prediction")
```
  Adjusted R squared = 0.54
  Fit= 0.15, CI= (-2.13,2.43)
  
## Model1 compared to Model3 

  
```{r}
anova(Model1,Model3)
```
  The P-value for comparison is 0.000004994 so we reject the null hypothesis, and conclude Model3 is better than model1. The adjusted R squared for Model3= 0.54, and the adjusted R squared for Model1 is 0.47, while the Model3 have a larger adjusted R squared makes it a better Model.
  